密文重复数据删除机制的频率攻击方法

### 2018-12-15 paper/threatModel.tex
ING | add threat model and begining of dis-attack

\chapter{威胁模型分析}
\label{sec:ThreatModel}

In this section, we formulate the threat model for our proposed frequency
analysis attacks against encrypted deduplication.

\section{Definitions}
\label{sec:ThreatModel-Definitions}

We first provide the definitions for our threat model. We model a plain file
as an ordered list of $n$ {\em logical plaintexts} (i.e., logical chunks
before deduplication), denoted by $\mathbf{M} = \langle \hat{M}^{(1)},
\hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$.  Each logical plaintext
$\hat{M}^{(i)}$ (where $1\le i\le n$) is encrypted via MLE into the
corresponding ciphertext $\hat{C}^{(i)}$, and all encrypted results of
$\mathbf{M}$ form a stream of $n$ {\em logical ciphertexts} $\mathbf{C} =
\langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$.  Note
that the logical ciphertexts in $\mathbf{C}$ are also ordered to reflect the
deduplication processing sequence of an encrypted deduplication storage
system.

Identical logical plaintexts and ciphertexts may appear at different positions
of $\mathbf{M}$ and $\mathbf{C}$, respectively.  We denote a unique plaintext
as $M$ (uniquely identified by its tag), which is encrypted via MLE to the
corresponding unique ciphertext $C$.  Each $M$ (resp. $C$) corresponds to one
or multiple identical copies of $\hat{M}^{(i)}$ (resp. $\hat{C}^{(i)}$).

% of $\mathbf{M}$ is
% independently encrypted into corresponding ciphertext $C$ via MLE, and all encrypted results

% A unique plaintext (or plaintext for short) $M$ has one or more copies in $\mathbf{M}$  
% Identical plaintexts may have multiple copies in $\mathbf{M}$, and we introduce unique plaintext  
% We define a unique plaintext as the plaintext that has unique content among other plaintexts of $\mathbf{M}$    
% Let $M$ and $C$ be a
% plaintext and its corresponding ciphertext, respectively; both of them are in
% units of chunks defined by deduplication.  We model a plain file before
% deduplication as an {\em ordered} list of $n$ plaintexts, denoted by
% $\mathbf{M} = \langle M^{(1)},  M^{(2)}, \ldots, M^{(n)}\rangle$.  Identical
% plaintexts may appear at different positions of $\mathbf{M}$, say $M^{(i)} =
% M^{(j)}$ for some $1\le i \neq j\le n$.   
% % Also, each plaintext can have the
% same or different chunk sizes due to fixed-size or variable-size chunking,
% respectively, and let $|M|$ denote the size of a plaintext $M$.  
% Let $M$ and $C$ denote a
% plaintext (i.e., a logical chunk before encryption) and its corresponding
% ciphertext (i.e., a logical chunk after encryption).  We model a plain file

\section{Adversarial Goals and Assumptions}
\label{sec:ThreatModel-Assumptions}

We consider an adversary that aims to infer a set of ciphertext-plaintext
pairs, denoted by \{$(C, M)$\}, with two specific goals:
\begin{itemize}[leftmargin=*]
\item
{\bf High inference rate:} A large fraction of correct ciphertext-plaintext pairs
are inferred, among all correct ciphertext-plaintext pairs (i.e., high recall or
low false negative rates in statistical terms).
\item
{\bf High inference precision:} A large fraction of ciphertext-plaintext pairs
are correct, among all inferred ciphertext-plaintext pairs (i.e., high precision
or low false positive rates in statistical terms).
\end{itemize}

We assume that the adversary is {\em honest-but-curious}, such that it can
passively monitor the stream of ciphertexts $\mathbf{C}$ being written to the
storage system and exploit different types of leakage information from
$\mathbf{C}$ (see Section~\ref{sec:leakage}).  Given the available leakage
information, the adversary aims to infer the original plaintext of each
ciphertext in $\mathbf{C}$ via a {\em ciphertext-only} attack.  It is possible
that the adversary knows a limited subset of ciphertext-plaintext pairs to
launch a known-plaintext attack, which further strengthens attack severity
\cite{li17}.  We do not consider the known-plaintext attack in this paper.

%We treat $\mathbf{C}$ as the {\em view} by the
%adversary and model different properties of the view

We assume that the adversary does not have access to any {\em metadata} that
contains the information about how chunks are operated and stored, as we do
not apply deduplication to the metadata and hence it can be protected by
traditional symmetric encryption.  Also, we assume that the adversary does not
have {\em active} capabilities, which can be independently prevented by
existing approaches. One example is that a malicious client may claim the
ownership of unauthorized files in client-side deduplication
\cite{harnik10,halevi11,mulazzani11}; it can be addressed by
proof-of-ownership \cite{halevi11,xu13,pietro12} or server-side deduplication
\cite{harnik10,li15}.  Another example is that a malicious storage system may
modify stored data; it can be detected by remote integrity checking
\cite{juels07,ateniese07}.

% In addition, $\mathcal{A}$ does not aim to infer if
% particular files have been stored \cite{harnik10, ritzdorf16}. Instead, we
% study the security implication based on the inferred contents over different
% types of files (see \S\ref{sec:case}).. 
% Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some
% well defined leakage $\mathcal{L}$, which includes the frequency, logical
% order and/or chunk size (\S\ref{sec:leakage}). 
% Note that $\mathcal{A}$ is specific to a {\em passive} adversary with content
% inference in mind. We do not assume $\mathcal{A}$ has {\em active}
% capabilities,

\section{Leakage Channels}
\label{sec:ThreatModel-Leakage}

We consider three types of leakage channels in encrypted deduplication storage
that enable an adversary to infer information:
\begin{itemize}[leftmargin=*]
\item
{\bf Frequency:}  Due to the deterministic nature of encrypted deduplication,
the frequency of each ciphertext in $\mathbf{C}$ before deduplication (i.e., 
the number of duplicate copies) can be mapped to that of its corresponding
plaintext in $\mathbf{M}$. 
% the size of each ciphertext in
% $\mathbf{C}$ is approximately equal to that of its corresponding plaintext in
% $\mathbf{M}$. In other words, the exact number of blocks (e.g., that are of size 16 bytes) in ciphertexts   
% the exact number of blocks in the plaintext equals the number of blocks in the ciphertext
% {\bf PC: if block cipher is used, it's not necessary that the
% plaintext has the same size as its ciphertext}.
%(e.g., \cite{douceur02, wilcox-ohearn08, bellare13b}) do not pad ciphertexts
%with additional data to avoid storage overhead, 
\item
{\bf Order:}  Some storage systems (e.g., \cite{xia11,lillibridge09,zhu08})
apply deduplication to the chunks in the same order as they appear in the
original file.  Thus, the order of ciphertexts in $\mathbf{C}$ can be mapped
to that of plaintexts in $\mathbf{M}$. 
\item
{\bf Size:}  Variable-size chunking (see Section~\ref{sec:background}) leads
to different chunk sizes of the ciphertexts.  If such ciphertexts are not
padded (to avoid storage overhead \cite{ritzdorf16}), the size of a ciphertext
in $\mathbf{C}$ can be mapped to that of its corresponding plaintext in
$\mathbf{M}$.    
\end{itemize}

%We also consider other leakage channels that are specific to real-world
%deduplication storage systems. First, {\em order leakage} exposes the logical
%order of each plaintext, and it is available for the systems
%\cite{xia11,lillibridge09,zhu08} that aim for high performance and operate
%the deduplication of chunks in the same order as these chunks appear in
%original files; this implies that the logical order of ciphertext in
%$\mathbf{C}$ exactly reflects that of its corresponding plaintext. Second,
%{\em size leakage} exposes the chunk size of each plaintext, since some
%systems \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage
%overhead and do not pad ciphertexts with any additional data; this
%implies that the size of ciphertext in $\mathbf{C}$ exactly equals that
%of its corresponding plaintext.

In addition, the adversary has access to some {\em auxiliary information} that
presents the ground truth about the data characteristics correlated with
$\mathbf{M}$. Note that the availability of auxiliary information is necessary
for any inference attack \cite{kumar07,li17,grubbs17,zhang16b,kellaris16,ritzdorf16,naveed15,cash15,islam12}.
In this work, we consider the auxiliary information as an ordered list of
previously known plaintexts (e.g., old user backups or VM disk images),
denoted by $\mathbf{A}$.  Clearly, the attack severity depends on the
correlation between $\mathbf{A}$ (i.e., the previously known plaintexts) and
$\mathbf{M}$ (i.e., the plaintexts that are to be inferred).  Our focus is not
to address how an adversary can obtain auxiliary information, possibly due to
careless data release \cite{careless-release}, stolen storage devices
\cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, given
such information, we investigate how the available auxiliary information,
combined with the leakage channels, bring information leakage from encrypted
deduplication.

We focus on frequency analysis \cite{alkadit92} as the attack methodology.
Classical frequency analysis sorts the unique ciphertexts in $\mathbf{C}$ and
the unique plaintexts in $\mathbf{A}$ by {\em frequency} (i.e., the number of
identical copies corresponding to each unique ciphertext or unique plaintext). 
It then relates each unique ciphertext in $\mathbf{C}$ with the unique
plaintext in $\mathbf{A}$ that has the same frequency rank. In the following
sections, we design sophisticated frequency analysis attacks against encrypted
deduplication.

% Frequency analysis is a cryptanalysis primitive to relate the ciphertexts in $\mathbf{C}$  with the plaintexts in $\mathbf{M}$. Specifically, it sorts ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively, and maps each ciphertext to the plaintext that has the same frequency rank. Building on the classical version of frequency analysis, we show how to exploit leakage channels to strengthen its severity against encrypted deduplication.

% infer ciphertext-plaintext pairs from $\mathbf{C}$ and $\mathbf{A}$. 
 % Specifically, the adversary

% It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext. 
% The more correlated to $\mathbf{M}$,

% Our focus is not to address its availability, which is due to careless data release \cite{careless-release}, stolen storage devices \cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, we show how an adversary can launch inference attacks based on the available auxiliary information $\mathbf{A}$.

% Our focus is not to address how to obtain accurate auxiliary information, which we pose as future work; instead, given the available auxiliary information, we study how an adversary can design a severe attack based on frequency analysis and how we can defend against the attack
% Some available auxiliary information has been demonstrated to be necessary for inference attacks  and we consider the auxiliary information $\mathbf{M}$ as a complete user backup, file system snapshot or VM disk image in plaintext. The rationale of its availability is that the adversary can obtain the original data from  We emphasize that the auxiliary information $\mathbf{M}$ does not need to be identical with the original file of $\mathbf{C}$. In other words, $\mathbf{M}$ may not have the
% same number of chunks with $\mathbf{C}$, or its $i$-th chunk $M^{\langle i \rangle}$ may not be the plaintext of $C^{\langle i \rangle}$ or even not mapped into $\mathbf{C}$. 
% {\bf PC: give the background on frequency analysis.}

% We assume that the adversary can take advantage of some   for attacks. The auxiliary information , and it has been demonstrated for necessity in inference attacks . In this work,

% In addition, the adversary can exploit other deduplication-specific leakage channels.

% effectiveness of inference attacks. First, we consider {\em size leakage}, meaning that the adversary can derive the size of a plaintext directly based on the corresponding ciphertext: ${\sf s}(C) = |M|$, where $C$ is the encryption of $M$.

% deduplication-specific leakage channels.

% We target inference attacks against {\em backup workloads}, which refer to the copies of primary data (e.g., application states, file systems, and virtual disk images) over time. The recent technology trend \cite{douglis17} suggests to create full backups (that store the complete data of the primary source) over traditional incremental backups (that only store the changes of data since the last full backup), so as to mitigate the overhead in restoring earlier (full) backups. Thus, we focus on inferring information from different versions of full backups (or backups for short) that are created based on the same primary data source at different times.

% They can be created as either weekly full backups (that store the complete data of the primary source) or daily incremental backups (that only store the changes of data since the prior full backup). Informed by the technology trend , we focus on full backups (or {\em backups} for short). Specifically, we aim to infer information from different versions of backups that are created based on the same primary data source yet at different times.

% To launch attacks, we assume that $\mathcal{A}$ is an ``{\em honest-but-curious}'' adversary that can compromise the server hosting deduplication service, while it cannot establish a long-term presence for attack. Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some well defined leakage $\mathcal{L}$, which includes the frequency, logical order and/or chunk size (\S\ref{sec:leakage}). Formally, we define these leakage channels based on a target victim file $\mathbf{M}_{\rm t}$:

% \begin{itemize}[leftmargin=*]
% 	\item  {\bf Frequency leakage}: $\mathcal{L}_{\rm freq} = \{(C, {\sf freq}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-frequency pairs, where $C$ is the encryption of some plaintext chunk $M$ in $\mathbf{M}_{\rm t}$, and each pair $(C, {\sf freq}(M))$ leaks the corresponding frequency of $M$.

% 	\item  {\bf Order leakage}: $\mathcal{L}_{\rm order} = \{(C, {\sf ord}(M)): M\in\mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ associates each ciphertext chunk $C$ with a set ${\sf ord}(M)$ of logical orders, at which the copies of its original chunk $M$ appear in $\mathbf{M}_{\rm t}$. Note that order leakage {\em implies} frequency leakage, since the logical orders of each chunk copy inherently includes the number of times the corresponding chunk appears.

% 	\item  {\bf Size leakage}: $\mathcal{L}_{\rm size} = \{(C, {\sf size}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-size pairs, where each pair leaks the size of the original chunk of $C$.
% \end{itemize}

% In addition, $\mathcal{A}$ can take advantage of the {\em auxiliary information} $\mathbf{M}_{\rm a}$ that presents the ground truth about the frequency, size and order information about plaintext chunks. Some available auxiliary information is necessary for inference attacks , and we focus on validating our attacks with the auxiliary information obtained from different types of storage workloads (see \S\ref{sec:dataset}).

% Acquiring the above capabilities, $\mathcal{A}$'s primary goal is to recover the plaintext chunks in the target file $\mathbf{M}_{\rm t}$. More formally, given the leakage $\mathcal{L}$ (that can be some combination of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$) and the auxiliary information $\mathbf{M}_{\rm a}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm a}) \rightarrow \mathcal{R}.$ Each output pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.

% identify the ciphertext-plaintext chunk pairs about $\mathbf{M}_{\rm tar}$. More formally, given the leakage $\mathcal{L}$ (that can be some combinations of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$), and auxiliary information $\mathbf{M}_{\rm aux}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm aux}) \rightarrow \mathcal{R}.$ Each pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.

% a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07};

% and it is a correct inference by $\mathcal{A}$ if $C$ is the actual encryption of $M$, i.e., $(M, C) \in \mathcal{E}$.

% We measure the success of attacks in several ways. The {\em raw inference rate} is the percentage of ciphertext chunks (including duplicates) that are inferred correctly over the total number of ciphertext chunks in the target information. For example, if the adversary correctly infers a ciphertext-plaintext chunk pair $(C, M)$ and the ciphertext chunk $C$ accounts for a fraction of 10\% in the target information, then the raw inference rate will be at least 10\%.

% We assume the adversary can eavesdrop the deduplication processing (e.g., comparison operation of fingerprints) of all ciphertext chunks in a victim file (called {\em target information}); on the other hand, it cannot access related metadata that can be protected by traditional encryption \cite{li17}. 
% the same and different private sources, as well as some public source .

% Note that $\mathcal{A}$ is specific to a passive adversary with content recovery in mind. We do not abstract $\mathcal{A}$ with active capabilities, since these threats can be protected by existing approaches. For example, a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07}; a malicious client may cheat owning a particular file \cite{harnik10,halevi11,mulazzani11}, yet it can be addressed by proof of ownership \cite{halevi11} or enforcing server-side deduplication \cite{li15}.

>>>>

\chapter{威胁模型}
\label{sec:ThreatModel}
本章为针对加密重复数据删除的频率分析攻击制定了威胁模型。

\section{威胁模型定义}
\label{sec:ThreatModel-Definitions}

本文分别使用$M$和$C$来表示明文数据块（即加密前的逻辑数据块）及其对应的密文数据块（即加密后的逻辑数据块）；$|M|$和$|C|$来表示明文数据块（即加密前的逻辑数据块）的大小及其对应的密文数据块（即加密后的逻辑数据块）的大小。

首先将普通文件建模为由$n$个逻辑明文数据块构成的有序列表（即重复数据删除之前的逻辑块），该列表记为$\mathbf{M} = \langle \hat{M}^{(1)}, \hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$。 每个逻辑明文数据块$\hat{M}^{(i)}$（其中$1\le i\le n$）通过MLE加密得到相应的密文数据块$\hat{C}^{(i)}$。由$\mathbf{M}$的所有加密结果形成由$n$个逻辑密文数据块组成的有序列表记为$\mathbf{C} = \langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$。在$\mathbf{C}$中的逻辑密文数据块也会被排序以反映加密重复数据删除存储系统中重复数据删除处理过程的顺序。

相同的逻辑明文和密文可能分别出现在$\mathbf{M}$和$\mathbf{C}$中的不同位置。 本文将一个唯一的明文数据块表示为$M$（通过其指纹的唯一性确定），通过MLE加密得到相应的唯一密文数据块$C$。每个$M$对应于$\hat{M}^{(i)}$的一个或多个相同副本，同理，每个$C$对应于$\hat{C}^{(i)}$的一个或多个相同副本。

\section{对手的目标和相关假设}
\label{sec:ThreatModel-Assumptions}

本文考虑存在一个对手，它准备以以下两个明确的目标为基准推断一组密文数据块-明文数据块对（用\{$(C, M)$\}表示）。

\begin{itemize}
    \item \textbf{推理率高:}

    在所有的正确密文数据块-明文数据块对中，推断出大部分正确的密文数据块-明文数据块对（即统计学上的高召回率或低阴性率）。

    \item \textbf{推理精度高:}

    在所有推断得到的密文数据块-明文数据块对中大部分的密文数据块-明文数据块对的配对是正确的（即统计术语中的高精度或低误报率）。
\end{itemize}

本文假设该对手是诚实但好奇的，它可以被动地监视密文数据块流$\mathbf{C}$被写入存储系统中的过程，并利用来自$\mathbf{C}$的不同类型的泄漏信息（参见章节：\ref{sec:ThreatModel-Leakage}）。鉴于可用的泄漏信息种类，对手仅可通过唯密文攻击的方法推断$\mathbf{C}$中每个密文数据块对应的原始明文数据块。当然，对手也有可能知道有限的密文数据块-明文数据块对的集合来发起已知明文攻击，这种情况进一步加深了攻击的严重性\citing{li2017information}。但在本文中不会考虑前述的已知明文攻击方式。因此，本文将$\mathbf{C}$视为对手所能观察到的的视图，并为该视图的不同属性建模。

本文假设对手无法访问任何包含有关如何操作和存储数据块的信息的元数据（由于不对元数据应用重复数据删除，因此可以通过传统的对称加密来保护这些元数据，这种操作可使得对手无法获知该类型的信息）。此外，本文假设对手没有主动对重复数据删除系统进行攻击的能力，因为这种问题可以通过现有方法予以阻止。例如是恶意客户端可以在客户端重复数据删除中声明对未授权文件拥有所有权\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}； 该问题可以通过所有权证明\citing{halevi2011proofs,xu2013weak,di2012boosting}或服务器端重复数据删除\citing{harnik2010side,li2015cdstore}予以解决。另一个例子是恶意存储系统可以修其改存储的数据；该问题可以通过远程完整性检查来进行检测和解决\citing{juels2007pors,ateniese2007provable}。

\section{三种信息的泄漏}
\label{sec:ThreatModel-Leakage}

本文在加密重复数据删除存储中考虑三种类型的泄漏方式，这些泄漏使得对手能够基于它们推断信息：

\begin{itemize}
    \item \textbf{频率：}

    由于加密重复数据删除的加密过程的确定性，重复数据删除前$\mathbf{C}$中每个密文数据块的频率（即重复副本数量）可以映射得到$\mathbf{M}$中相应明文数据块的频率。

    \item \textbf{顺序：}

    某些加密重复数据删除存储系统\cite{xia2011silo,lillibridge2009sparse,zhu2008avoiding}为了更高的运行性能，在存储密文数据块是保持了其对应的明文数据块的原始顺序。因此，$\mathbf{C}$中的密文的顺序可以映射到$\mathbf{M}$中的明文的顺序。

    \item \textbf{大小：}

    可变大小的数据块分块方法（参见章节：\ref{sec:background}）产生会产生各种不同大小的明文数据块，如果在对明文数据块进行加密前没有进行数据填充（为了避免增大存储开销\citing{ritzdorf2016information,douceur2002reclaiming,wilcox2008tahoe,keelveedhi2013dupless}），则产生的密文数据块大小与其对应的原始明文数据块大小一致（$\mathbf{C}$中的密文大小可以映射到$\mathbf{M}$中相应明文的大小）且密文数据块集合中的密文数据块也具有众多不同的大小。当然，该泄漏可以通过使用块密码算法使得明密文数据块大小不一致来避免。
\end{itemize}

除上述三种泄漏以外，对手还可以获得一些辅助信息，这些信息提供了与$\mathbf{M}$相关的数据特征的基本情况（任何推理攻击都必须提供辅助信息\citing{kumar2007anonymizing,li2017information,grubbs2016breaking,zhang2016all,kellaris2016generic,ritzdorf2016information,naveed2015inference,cash2015leakage,islam2012access}）。在这项工作中，将辅助信息视为先前已知的明文数据块（例如，通过旧用户备份或VM磁盘映像得到）构成的有序列表，由$\mathbf{A}$表示。显然，攻击有效性与严重性取决于$\mathbf{A}$（即先前已知的明文数据块）和$\mathbf{M}$（即要推断的明文数据块）之间的相关性。本文的重点不是解决对手如何获取辅助信息的问题。例如，可能是由于粗心的数据发布\citing{careless-release}、被的盗存储设备\citing{stolen-device}和云存储泄漏\citing{cloud-leakage}。相反，根据这些信息，本文研究了可以获得的的辅助信息如何与各种泄漏渠道相结合，给加密重复数据删除带来信息泄漏。

本文将频率分析\citing{al1992origins}作为攻击方法。经典频率分析对$\mathbf{C}$中的唯一密文数据块和$\mathbf{A}$中的唯一明文数据块按频率（即对应于每个唯一密文数据块或唯一明文数据块的相同副本的数量）进行排序。然后，简单的将$\mathbf{C}$中的每个唯一密文数据块与$\mathbf{A}$中具有相同频率等级的唯一明文数据块相关联。基本的频率分析攻击实际效果非常糟糕，在接下来的章节中，本文针对加密重复数据删除设计了较为复杂同时效性极高的频率分析攻击。

\section{本章小结}

本章介绍了针对重复数据删除的威胁模型的定义、本课题研究中将要用到的各种信息来源，以及本文攻击方案的假设的相关说明。
